---
title: "statistic with R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Descriptive Statistic

Data
```{r cars}
student.height <- c(100, 106, 121, 111, 109, 111, 103, 117, 114)
summary(student.height)
```

### Measurement of central tendance

```{r pressure, echo=FALSE}
Mean <- mean(student.height, trim = 0.1, na.rm = TRUE)
Median <- median(student.height)
Mode <- sort(table(student.height), decreasing = TRUE)[1]
print("Mean : ", Mean, "Median : ", Median, "Mode : ", Mode)
```

> option to trim the data. The argument trim = 0.1 (for example) will remove 10% data from the top and 10% from the bottom
> There is no direct command in R Basics to find the mode

### Measurement of Variation

```{r cars}
Range <- range(student.height)
Quantile <- quantile(student.height)
IQR <- IQR(student.height)
Standard_D <- sd(student.height)
Min <- min(student.height)
Max <- max(student.height)
print("Range : ", Range, "Quantile : ", Quantile, "Standard_D : ", Standard_D, , "IQR : ", IQR)

```
>quartile : 
  * 0% = Lowest value, 
  * 25% = First quartile (Q1), 
  * 50% = Median (Q2), 
  * 75% = Third quartile (Q3), 
  * 100% = Highest value
  
  
```{r pressure, echo=FALSE}
boxplot(student.height, main = "Boxplot of student.height (cm)", col = "blue",border = "brown", horizontal = TRUE, xlab = "student height in Cm",notch = FALSE)
```


## Data Visualization


```{r pressure, echo=FALSE}
library(palmerpenguins)
data("penguins")
head(penguins)
```
```{r pressure, echo=FALSE}
str(penguins)
```

```{r pressure, echo=FALSE}
student.height <- c(100, 106, 121, 111, 109, 111, 103, 117, 114)
student.weigth <- c(40, 46, 61, 51, 49, 51, 43, 57, 64)
par(mfrow=c(1,2))
plot(student.height, student.weigth, main="Arrival vs Departure Delay", 
 xlab="Arrival Delay", ylab="Departure Delay", pch=3)
plot(student.height, student.weigth, main="Arrival vs Departure Delay", 
 xlab="Arrival Delay", ylab="Departure Delay", pch=3)
```
```{r pressure, echo=FALSE}
hist(student.weigth, breaks = 10)
```

```{r pressure, echo=FALSE}
boxplot(student.height)
```

hist(distance, breaks = 10